Matching Bullets

### 2015-12-12 imaging-paper.Rnw
and now it's latexing again

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}
\begin{figure}[hbtp]
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch-rgl}\hh{Different view of the manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}

@@

\end{enumerate}

>>>>

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}Manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}
\end{figure}
\begin{figure}[hbtp]
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch-rgl}Different view of the manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}
\end{figure}

@@
